---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# summarizetaskview


Way to quickly summarize info from a task view (or other list of packages)

This was inspired by [Jonathan Chang's post](https://jonathanchang.org/blog/what-r-package-for-phylogenetics-is-the-most-popular/) about downloads for different phylogenetics-related R packages as well as my long term curiosity about how packages in our area. It was also (I now realize after [Maëlle Salmon's](https://twitter.com/ma_salmon) tweet about this, inspired by this [rOpenSci hackathon project, packagemetrics](https://github.com/ropenscilabs/packagemetrics)). It depends on [goodpractice](https://cran.r-project.org/web/packages/goodpractice/vignettes/goodpractice.html) (thanks to [Auriel Fournier](https://twitter.com/RallidaeRule) for pointing to that package) and also uses the packages crandb, cranlogs, ggplot2, lubridate, ctv, packagemetrics, and parallel.



```{r table, echo=FALSE, results='asis'}
library(knitr)
library(summarizetaskview)
all_package_results <- t(sapply(all_packages, summarize_goodness))
kable(all_package_results)
```

```{r figures, echo=FALSE, warnings=FALSE, fig.height=2, fig.width=3}
for (package.index in seq_along(all_packages)) {
  cat(paste0("\n## ", (all_packages[[package.index]])$package_info$name), "\n")
  print(suppressWarnings(plot_package_check(all_packages[[package.index]], comparison="ape")))
}
```
